\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
Adjusted abstract

    We introduce hereafter \uwds, a novel framework for \emph{cascading}
    spatio-temporal situation assessment in robotics. \uwds allows programmers
    to represent the robot's environment as real-time distributed data
    structures, containing both scene graphs (for 3D representation of geometries)
    and timelines (for representation of temporal events). \uwds supports
    \emph{cascading} representations: the environment is viewed as a set of
    \emph{worlds} that can each have different spatial and temporal
    granularities, and may depend on each others.

    \uwds also provides a set of high-level client libraries and tools to introspect
    and manipulate the environment models.

>>>>

    We introduce \uwds, a novel lightweight framework for \emph{cascading
    spatio-temporal situation assessment} in robotics. \uwds allows programmers
    to represent the robot's environment as real-time distributed data
    structures, containing both scene graphs (for representation of 3D
    geometries) and timelines (for representation of temporal events). \uwds
    supports \emph{cascading} representations: the environment is viewed as a
    set of \emph{worlds} that can each have different spatial and temporal
    granularities, and may depend on each others.  \uwds also provides a set of
    high-level client libraries and tools to introspect and manipulate the
    environment models.
